Regression Analysis—Interactions—Reviewing Editor

### 2019-07-25 figures/regression_analysis/regression_bre_only_analysis.rmd
removed mention of initial submissions, which relied on senior editor gender. Also fixed stargazer table labels and converted estimates to odds ratios

elife$ca_continent <- relevel(elife$ca_continent, ref = "North America")
elife$fa_continent <- relevel(elife$fa_continent, ref = "North America")
elife$la_continent <- relevel(elife$la_continent, ref = "North America")
elife$se_continent <- relevel(elife$se_continent, ref = "North America")

@@

elife$la_institution_rank <- with(elife, ifelse(la_institution_rank == "Top", "Top", "Sandard/Unranked/Unknown"))
elife$ca_institution_rank <- with(elife, ifelse(ca_institution_rank == "Top", "Top", "Sandard/Unranked/Unknown"))

@@

### Define initial and full submissions
```{r}
# First, filter the data by removing the observations from Antarctica 
# add a variable for "included"
initial_submissions <- elife %>% filter(initial_decision_made)
initial_submissions$included <- with(initial_submissions, initial_decision_made & ca_continent != "Antarctica" & !is.na(ca_institution_rank) & !is.na(ca_gender) & !is.na(ca_se_dist) & !is.na(se_gender))

full_submissions <- elife %>% filter(full_decision_made)
full_submissions$included <- with(full_submissions, la_continent != "Antarctica" & fa_continent != "Antarctica" & !is.na(la_gender) & la_gender != "UNK" & composition != "Uncertain" & !is.na(la_reviewer_dist) & !is.na(la_reviewer_dist_zero) & !is.na(la_institution_rank) & !is.na(la_continent) & !is.na(fa_gender))
```

### Construct the initial submissions model
```{r}
initial_model <- glm(encouraged ~ submission_year + submission_type + ca_gender +  ca_institution_rank + ca_continent + I(ca_se_dist / 1000000) + ca_se_dist_zero + ca_se_dist_zero, data = subset(initial_submissions, included), family = "binomial")
summary(initial_model)
```

### Construct a regression table for the 
```{r}
initial.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "ca_genderM" = "Corr. Author is Male",
               "ca_genderUNK" = "Corr. Author Gender UNK",
               "ca_institution_rankTop" = "Corr. Author Inst. Top 50",
               "ca_institution_rankStandard/Unranked/Unknown" = "Corr. Author Inst. Below 200",
               "ca_continentAfrica" = "Corr. author from Africa",
               "ca_continentAsia" = "Corr. author from Asia",
               "ca_continentEurope" = "Corr. author from Europe",
               "ca_continentOceania" = "Corr. author from Oceania",
               "ca_continentSouth America" = "Corr. author from South America",
               "se_genderM" = "Senior Editor is Male",
               "I(ca_se_dist/1e+06)" = "Geographic distance (1000s km)",
               "ca_se_dist_zeroTRUE" = "Geographic distance is zero",
               "ca_genderM:se_genderM" = "Corr. author male * Senior editor male",
               "ca_genderUNK:se_genderM" = "Corr. author UNK * Senior editor male"

               )

out <- capture.output(stargazer(initial_model, 
                                ci = T, 
                                align = T, 
                                covariate.labels = initial.cov.labels, 
                                model.names = T,
                                style = "ajs"
                                ))

#cat(paste(out, collapse = "\n"), "\n", file="~/Desktop/encourage_model.txt", append=F)
out
```

### Construct the initial regression plot
```{r}
initial_reg_plot <- plot_model(initial_model, 
           vline.color = "black", 
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = initial.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "Encouragement of initial submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

initial_reg_plot
```

@@

### Construct the plot for full submissions
```{r}
full.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankStandard/Unranked/Unknown" = "Last Author Inst. Below 200",
               "la_institution_rankTop" = "Last Author Inst. Top 50",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America",
               "I(la_bre_dist/1e+06)" = "Dist. between author and rev. editor (1000km)",
               "I(la_reviewer_dist/1e+06)" = "Sum of author-reviewer distance (1000km)",
               "la_reviewer_dist_zeroTRUE" = "Total dist. between author and reviewers is zero",
               "la_bre_dist_zeroTRUE" = "Dist. between author and rev. editor is zero",
               "author_bre_interactionFemale Author, Male Rev. Editor" = "Last author female - male rev. editor",
               "author_bre_interactionFemale Author, Female Rev. Editor" = "Last author female - female rev. editor",
               "author_bre_interactionMale Author, Female Rev. Editor" = "Last author male - female rev. editor",
               "author_bre_interactionMale Author, Male Rev. Editor" = "Last author male - male rev. editor",
               "composition_adjAll Women" = "All Female Reviewers",
               "composition_adjMixed" = "Mixed Reviewers"
               )

@@

```{r}
library(stargazer)
stargazer(full_model,
          covariate.labels = full.cov.labels,
          t.auto = F,
          p.auto = F,
          type = "latex",
          font.size = "small",
          style = "ajs")
```

>>>>

elife$fa_continent <- relevel(elife$fa_continent, ref = "North America")
elife$la_continent <- relevel(elife$la_continent, ref = "North America")

@@

elife$la_institution_rank <- with(elife, ifelse(la_institution_rank == "Top", "Top", "Sandard/Unranked/Unknown"))

@@

### Define initial and full submissions
```{r}
full_submissions <- elife %>% filter(full_decision_made)
full_submissions$included <- with(full_submissions, la_continent != "Antarctica" & fa_continent != "Antarctica" & !is.na(la_gender) & la_gender != "UNK" & composition != "Uncertain" & !is.na(la_reviewer_dist) & !is.na(la_reviewer_dist_zero) & !is.na(la_institution_rank) & !is.na(la_continent) & !is.na(fa_gender))
```

@@

### Construct the plot for full submissions
```{r}
full.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankTop" = "Last Author Inst. Top 50",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America",
               "I(la_bre_dist/1e+06)" = "Dist. between author and rev. editor (1000km)",
               "I(la_reviewer_dist/1e+06)" = "Sum of author-reviewer distance (1000km)",
               "la_reviewer_dist_zeroTRUE" = "Total dist. between author and reviewers is zero",
               "la_bre_dist_zeroTRUE" = "Dist. between author and rev. editor is zero",
               "author_bre_interactionFemale Author, Male Rev. Editor" = "Last author female - male rev. editor",
               #"author_bre_interactionFemale Author, Female Rev. Editor" = "Last author female - female rev. editor",
               "author_bre_interactionMale Author, Female Rev. Editor" = "Last author male - female rev. editor",
               "author_bre_interactionMale Author, Male Rev. Editor" = "Last author male - male rev. editor",
               "composition_adjAll Women" = "All Female Reviewers",
               "composition_adjMixed" = "Mixed Reviewers"
               )

@@

```{r}
library(stargazer)
stargazer(full_model,
          covariate.labels = full.cov.labels,
          t.auto = F,
          p.auto = F,
          ci = T, 
          align = T,
          apply.coef = exp,
          type = "latex",
          font.size = "tiny",
          style = "ajs")
```
